### 2013-09-17 research/paper/Theory/mathematical_model.tex
Updated 17 Sep

 One of the widely used mathematical model to predict the system response under galloping is the Quasi-steady state (QSS) model, incorporated by \cite{Parkinson1964} for a square cross section. The equation of motion of the body under galloping is given by Eq. \eqref{equationofmotion}. The forcing term $F_y$ is given by Eq.\eqref{lift equation}.

@@

\cite{Joly2012} introduced  an addition of a sinusoidal forcing function to the hydrodynamic forcing. This enables to model to provide accurate predictions even at low mass ratios where galloping excitation is suppressed or not present. In this study, the forcing due to VIV is incorporated using a sinusoidal forcing function $F_0\sin{\omega_{s}t}$ added to the RHS of the equation. $\omega_{s}$ and $F_0$ represents shedding frequency and the maximum force due to shedding respectively. Thus, the final equation is given by Eq. \eqref{final_equation_motion}.

@@

 The dissipated power due to the mechanical damping represents the ideal potential amount of harvested power output. Therefore the mean power output could be given by Eq. \eqref{power}.

@@

 \input{../figure/cy_vs_theta}
 \vspace{20mm}
 \input{../figure/coefficient-table}

@@

Shedding frequency $\omega_s$, was set to $0.98$ winch was obtained by performing a power spectral analysis of the stationary data at $0^0$. Stationary $C_y$ data were obtained at different angles of attack ranging from $0^0$ to $16^0$. The average power was obtained by using Eq. \eqref{power}

and the averaging was done over no less than 20 galloping periods. Predictions of power output at Re=22300 were obtained using coefficients for curve fitting $C_y$ (\ref{table:cy-coefficients}) from \cite{Parkinson1964} in order to provide a comparison between high and low Reynolds numbers. $m^*$ was kept at 1163 for \reynoldsnumber=22300 (Similar as \cite{Parkinson1964}) and $m^*=20$ for \reynoldsnumber=165. These parameters  were used throughout this study unless otherwise specified.

@@

 The computational domain consists of 690 quadrilateral macro elements where majority of the elements were concentrated near the square section. A freestream condition was given to the inlet, top and bottom boundaries and the normal velocity gradient was set to zero at the outlet. A convergence study was performed by changing the order of the polynomial ($p$-refinement) at $U^*=40$ and Re $165$. A 9th order polynomial together with a time step of $\frac{\Delta tU}{D}=0.001$ was sufficient to ensure an accuracy of $2\%$ with regards to amplitude of oscillation.

>>>>

 One of the widely used mathematical model to predict the system response under galloping is the Quasi-steady state (QSS) model, incorporated by \cite{Parkinson1964} for a square cross section. The equation of motion of the body under galloping is given by Eq.\eqref{equationofmotion}. The forcing term $F_y$ is given by Eq.\eqref{lift equation}.

@@

\cite{Joly2012} introduced  an addition of a sinusoidal forcing function to the hydrodynamic forcing. This enables to model to provide accurate predictions even at low mass ratios where galloping excitation is suppressed or not present. In this study, the forcing due to VIV is incorporated using a sinusoidal forcing function $F_0\sin{\omega_{s}t}$ added to the RHS of the equation. $\omega_{s}$ and $F_0$ represents shedding frequency and the maximum force due to shedding respectively. Thus, the final equation is given by Eq.\eqref{final_equation_motion}.

@@

 The dissipated power due to the mechanical damping represents the ideal potential amount of harvested power output. Therefore the mean power output could be given by Eq.\eqref{power}.

@@

 \input{../figure/cy_vs_theta}

 \input{../figure/coefficient-table}

@@

Shedding frequency $\omega_s$, was set to $0.98$ which was obtained by performing a power spectral analysis of the stationary data at $0^0$. Stationary $C_y$ data were obtained at different angles of attack ranging from $0^0$ to $16^0$. The average power was obtained by using Eq.\eqref{power}

and the averaging was done over no less than 20 galloping periods. Predictions of power output at Re=22300 were obtained using coefficients for curve fitting $C_y$ (Table (\ref{table:cy-coefficients})) from \cite{Parkinson1964} in order to provide a comparison between high and low Reynolds numbers. $m^*$ was kept at 1163 for \reynoldsnumber=22300 (Similar as \cite{Parkinson1964}) and $m^*=20$ for \reynoldsnumber=165. These parameters  were used throughout this study unless otherwise specified.

@@

 The computational domain consists of 690 quadrilateral macro elements where majority of the elements were concentrated near the square section. A freestream condition was given to the inlet, top and bottom boundaries and the normal velocity gradient was set to zero at the outlet. A convergence study was performed by changing the order of the polynomial ($p$-refinement) at $U^*=40$ and \reynoldsnumber=$165$. A $9^{th}$ order polynomial together with a time step of $\frac{\Delta tU}{D}=0.001$ was sufficient to ensure an accuracy of $2\%$ with regards to amplitude of oscillation.

### 2013-09-17 research/paper/introduction/intro-1.0.tex
Updated 17 Sep

The search for alternate energy sources which could be categorised  under the "green" label has become important area of research in the modern word. Solar, wind power and wave power are some of the examples of these sources.  Recently,a new branch of research has been developing to extract energy from flow induced vibrations(\cite{Bernitsas2008a-concept}). It has been hypothesized that this technique may work efficiently in areas where regular turbines cannot.

An elastically mounted slender structure such as cylinders which  are susceptible to flow-induced vibrations has the potential for energy extraction. With regards to a slender body two common types of   flow induced vibrations are Vortex Induced Vibrations (VIV) and aeroelastic galloping. Significant research has been carried out by Bernitsas and his team on extracting useful energy from VIV. Some of their significant work includes investigating the influence  of physical parameters such as mass ratio, Reynolds number, mechanical properties(\cite{Raghavan2010a} ,\cite{Lee2011b}) and location (effect of the bottom boundary) (\cite{Raghavan2009}). However,the possibility of extracting energy using aeroelastic galloping has not been thoroughly investigated. Some theoretical work was carried out by (\cite{Barrero-Gil2010a}). Utilizing galloping may be a more viable method to harness energy from flow induced vibrations as it is not bounded by a narrow "lock-in" range of reduced velocities(ratio between the freestream velocity and the product of the natural frequency of the system and the characteristic length). This study further explores the possibility of harnessing energy from flow induced vibrations using aeroelastic galloping.

Energy harvesting systems have high damping ratios because the energy generator (e.g electrical generator) puts a significant amount of damping into the system. Therefore it is crucial to investigate  the behaviour of aeroleastic galloping scenarios at high damping ratios in order to optimise the system to obtain a acceptable power output.Hence the focus of this paper is concentrated on investigating the mechanical power output of high-damped galloping systems.

According to \cite{Paidoussis2010},\cite{Glauert1919} has provided a criterion for galloping by considering the auto-rotation of an aerofoil.  \cite{DenHartog1956}  has provided a theoretical explanation for galloping for iced electric transmission lines. A non-linear theoretical aeroelastic model to predict the response of galloping was developed by \cite{Parkinson1964} based on the quasi-steady state (QSS) theory. Experimental lift and drag data on a fixed square prism at different angles of attack were used as an input for the theoretical model. It essentially used a curve fit of the transverse force to predict the galloping response. The study managed to achieve a good agreement with experimental data. The QSS model equation when solved using analytically using sinusoidal solution method cannot predict cases with low mass ratios  .\cite{Joly2012} have observed that finite element simulations shows a sudden change in amplitudes  below a critical values of the mass ratio. The Parkinson's equation was essentially modified to account for the vortex shedding and managed to produce the effects to the amplitude at low mass ratios.
\cite{Barrero-Gil2010a} have investigated the possibility of extracting power from vibrations caused by galloping using quasi-steady state theory. In the conclusions of that paper it was pointed out that in order to obtain a high power to area ratio, the mass-damping ($m^*\zeta$) parameter should be kept low. Another interesting conclusion was that energy conversion systems which uses galloping could operate over  a large range of flow velocities unlike VIV energy harvesting systems where the factor of energy conversion has a strong dependence on the incoming flow velocity.

>>>>

The search for alternate energy sources which could be categorised  under the ``green" label has become important area of research in the modern word. Solar, wind power and wave power are some of the examples of these sources.  Recently, a new branch of research has been developing to extract energy from flow induced vibrations(\cite{Bernitsas2008a-concept}). It has been hypothesized that this technique may work efficiently in areas where regular turbines cannot.

An elastically mounted slender structure such as cylinders which  are susceptible to flow-induced vibrations has the potential for energy extraction. With regards to a slender body two common types of   flow induced vibrations are Vortex Induced Vibrations (VIV) and aeroelastic galloping. Significant research has been carried out by Bernitsas and his team on extracting useful energy from VIV. Some of their significant work includes investigating the influence  of physical parameters such as mass ratio, Reynolds number, mechanical properties (\cite{Raghavan2010a} , \cite{Lee2011b}) and location (effect of the bottom boundary) (\cite{Raghavan2009}). However, the possibility of extracting energy using aeroelastic galloping has not been thoroughly investigated. Some theoretical work was carried out by (\cite{Barrero-Gil2010a}). Utilizing galloping may be a more viable method to harness energy from flow induced vibrations as it is not bounded by a narrow ``lock-in" range of reduced velocities(ratio between the freestream velocity and the product of the natural frequency of the system and the characteristic length). This study further explores the possibility of harnessing energy from flow induced vibrations using aeroelastic galloping.

Energy harvesting systems have high damping ratios because the energy generator (e.g electrical generator) puts a significant amount of damping into the system. Therefore it is crucial to investigate  the behaviour of aeroleastic galloping scenarios at high damping ratios in order to optimise the system to obtain a acceptable power output. Hence the focus of this paper is concentrated on investigating the mechanical power output of high-damped galloping systems.

According to \cite{Paidoussis2010}, \cite{Glauert1919} has provided a criterion for galloping by considering the auto-rotation of an aerofoil.  \cite{DenHartog1956}  has provided a theoretical explanation for galloping for iced electric transmission lines. A weakly non-linear theoretical aeroelastic model to predict the response of galloping was developed by \cite{Parkinson1964} based on the quasi-steady state (QSS) theory. Experimental lift and drag data on a fixed square prism at different angles of attack were used as an input for the theoretical model. It essentially used a curve fit of the transverse force to predict the galloping response. The study managed to achieve a good agreement with experimental data. The QSS model equation when solved analytically using sinusoidal solution method cannot predict cases with low mass ratios. \cite{Joly2012} have observed that finite element simulations shows a sudden change in amplitudes  below a critical values of the mass ratio. The Parkinson's equation was essentially modified to account for the vortex shedding and managed to produce the effects to the amplitude at low mass ratios.
\cite{Barrero-Gil2010a} have investigated the possibility of extracting power from vibrations caused by galloping using quasi-steady state theory. In the conclusions of that paper it was pointed out that in order to obtain a high power to area ratio, the mass-damping ($m^*\zeta$) parameter should be kept low. Another interesting conclusion was that energy conversion systems which uses galloping could operate over  a large range of flow velocities unlike VIV energy harvesting systems where the factor of energy conversion has a strong dependence on the incoming flow velocity.

### 2013-09-17 research/paper/results/results-2.3.tex
Updated 17 Sep

The stationary $C_y$ data obtained using flow simulations (Fig.\ref{cy ploynomial}(a))have a good agreement with data presented in \cite{Joly2012}. In comparison with the 7th order polynomial curve at \reynoldsnumber=22300 (Fig.\ref{cy ploynomial}(b))  several differences could be observed. The peak value of $C_y$ is  significantly low at \reynoldsnumber=165 ($C_y=0.05$ at $4^0$) in comparison with \reynoldsnumber=22300 ($C_y=0.57$ at $13^0$) . The inflection point present at \reynoldsnumber=22300 could not be observed at \reynoldsnumber=165. This agrees with the findings of \cite{Luo2003}. It was concluded by \cite{Luo2003} that hysteresis occur due to the inflection point found in the $C_y$ curve. Therefore hysteresis is not expected at \reynoldsnumber=165. The range of the incident flow angles where $C_y$ remain positive is narrow at \reynoldsnumber=165 ($0^0 <\theta \leq$ $6^0$) compared to \reynoldsnumber=22300 ($0^0 <\theta \leq 15^0$). This feature is what sustains galloping and power is transferred from the fluid to the supporting structure within this range of incident angle because fluid forces are acting in the direction of travel of the oscillating cylinder. Incident angles beyond this range actually suppresses the galloping and power goes in the opposite direction. Therefore due to the overall smaller $C_y$ and narrow range of angles where $C_y$ is positive for \reynoldsnumber=165 compared to \reynoldsnumber=22300 leads one to expect a significant reduction in power at\reynoldsnumber=165 compared to \reynoldsnumber=2230.

@@

 The data presented in Fig.\ref{fig:uncollapsed_data} for various damping ratios ,$\zeta$, can be collapsed into a single line for a for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve)  curve could be obtained for the velocity amplitude  and power were plotted as a function of  non dimensionalised  damping constant $c\rho\mathcal{A}U$ 
(Fig \ref{fig:collpased_data} (a),(b),(c) and (d)).  This further emphasizes that the galloping system is not frequency dependent. It is possible to obtain a different similar power output at different values of \ustar when the damping constant, $c\rho\mathbb{A}U$, is kept fixed. An example of this case, as shown in Fig.\ref{fig:time_hostory_velocity_same_power}, clearly show that this is a result of similar velocity amplitudes between cases if one were to disregard the high frequencies due to shedding. As mentioned earlier, it is the transverse velocity that determines the energy provided by the fluid forcing and the mechanical damping.

@@

 Power could be expressed as the product of force and velocity. Therefore the transferred power form fluid-to-body could be expressed as $P_t=F_y\dot{y}$. Similarly the dissipated power due to the mechanical damping could be expressed as $P_d=(c\dot{y})\dot{y}$. The time average of these two quantities should be equal due to energy conservation, provided that the mechanical friction is neglected . Analysing the  time histories of $P_t $ and $P_d$ at key regions (Fig.\ref{fig:regions_1}) on the mean power vs $U^*$ provides a detailed explanation for the variation of the output powe when the reduced velocity is increased. The key regions consists of region 1 where the $P_m$ increases with \ustar, region 2 where $P_m$ becomes maximum and region 3 where $P_m$ decreases with \ustar. It has been established earlier that the damping factor is a function of $U^*$. Therefore it could be derived that $U^*$ is inversely proportional to damping coefficient. Hence the damping coefficient reduces when you move from region 1 to 3.Fig \ref{fig:lift_curves} (a) shows that $C_y$ and therefore instantaneous force rises until $4^0$ where it peaks and then falls and at around $6^0$ becomes negative. Maximum amount of power could be transferred within the peak region. At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$.Data at $\zeta=0.1$, $m^*=40$ and \reynoldsnumber=165 (Fig.\ref{fig:power_time_histories}) are analysed as and example.

@@

 At region 1 where $U^*=90$ the damping constant is high and a clear sinusoidal signal could be observed for both $P_d$ and $P_t$ in Fig. \ref{fig:power_time_histories} (a). Fig.\ref{fig:power_time_histories} (d) and (g) shows that $\theta$ is in line or in phase with $F_y$.  The velocity amplitude in this case is small and the equivalent incident angle within the range where the hydrodynamic force increases with the incident angle (i.e. $0<\theta \leq < 4^0$ in \ref{fig:lift_curves}) Hence both $P_d$ and $P_t$ becomes sinusoidal. In this case, power output is limited by the low fluid forces present at low incident angles. In other words damping is significantly high and extracts a lot of power that the velocity amplitude could not grow where the forcing  is significant to produce high level of power.

  At region 3 ($U^*= 400$) `$c$' is low in comparison with region 1 and 2 which leads to a low mean power output. Fig.\ref{fig:power_time_histories} (c) shows that $P_t$ becomes negative over some portion of the cycle. This is because $\theta$  passes the point where both $\theta$ and $C_y$ (therefore $F_y$) are positive. The high velocity amplitude leads to the equivalent incident angle $\theta$, in this case to exceed the range where $C_y$ is positive (i.e. $0<\theta<6^0$ in Fig.\ref{cy ploynomial} (a)). In this portion of the cycle the hydrodynamic force actually opposes the direction of travel and power is transferred from the structure to the fluid during those times. From and energy perspective, the mechanical damping is not sufficient to remover the energy transferred from the fluid to the structure during other times of the cycle because $c\rho\mathcal{A}U$ is substantially low. Therefore this excess energy is transferred back to the fluid as depicted by the negative region of $P_d$ in \ref{fig:power_time_histories} (c)

@@

The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}) was constant beyond $m^*=30$. However, at $m^* \leq 30$ an effect of $m^*$ it could be observed. Not only the peak value but overall reduction in the mean power could be observed when $m^*$ was reduced. c When galloping excitation is suppressed al low $m^*$, the system will exhibit a weak response as a result of forcing from vortex shedding. This was also reported by \cite{Joly2012} where galloping amplitude was reduced at low $m^*$. The suppression of galloping as $m^*$ is reduced can be explained by looking at the difference between the instantaneous power transfer between fluid to the structure $P_t$ and the power taken out by the mechanical damping $P_t$ in Fig.\ref{fig:power_time_histories}. While the time average of both quantities are the same, instantaneously they are not. Therefore the mechanical system is required to store power in certain points of the cycle and release it at another portion of the cycle. In cases where $m^*$ is very low, the system lack adequate inertia to store this power which leads to suppression of galloping.

@@

\subsection{Comparison with FSI simulations}
 Similar trends were captured for both displacement and velocity amplitudes between QSS and FSI simulations (Fig. \ref{fig:FSI_QSS_compare}(a) and \ref{fig:FSI_QSS_compare}(b)). Quantitatively a large discrepancy (average of $30\%$) could be observed between QSS and FSI data. Therefore the power also becomes significantly low in FSI data (Fig.\ref{fig:FSI_QSS_compare}(c)). However, the FSI data (Fig.\ref{fig:FSI_QSS_compare} (c)) were able to produce the main the rise and the fall of mean power when $U^*$ was increased. The reasoning behind this fact is that galloping is weak at Re 165  and therefore fluid damping has a significant effect. It was reported by \cite{Barrero-Gil2009} that galloping only starts to occur ar Re $\geq 159$. As power is function of $(\dot{y})^2$ the error between QSS and FSI power becomes significantly large.

>>>>

The stationary $C_y$ data obtained using flow simulations (Fig.\ref{cy ploynomial}(a)) have a good agreement with data presented in \cite{Joly2012}. In comparison with the 7th order polynomial curve at \reynoldsnumber=22300 (Fig.\ref{cy ploynomial}(b))  several differences could be observed. The peak value of $C_y$ is  significantly low at \reynoldsnumber=165 ($C_y=0.05$ at $4^0$) in comparison with \reynoldsnumber=22300 ($C_y=0.57$ at $13^0$) . The inflection point present at \reynoldsnumber=22300 could not be observed at \reynoldsnumber=165. This agrees with the findings of \cite{Luo2003}. It was concluded by \cite{Luo2003} that hysteresis occur due to the inflection point found in the $C_y$ curve. Therefore hysteresis is not expected at \reynoldsnumber=165. The range of the incident flow angles where $C_y$ remain positive is narrow at \reynoldsnumber=165 ($0^0 <\theta \leq$ $6^0$) compared to \reynoldsnumber=22300 ($0^0 <\theta \leq 15^0$). This feature is what sustains galloping and power is transferred from the fluid to the supporting structure within this range of incident angle because fluid forces are acting in the direction of travel of the oscillating cylinder. Incident angles beyond this range actually suppresses the galloping and power goes in the opposite direction. Therefore due to the overall smaller $C_y$ and narrow range of angles where $C_y$ is positive for \reynoldsnumber=165 compared to \reynoldsnumber=22300 leads one to expect a significant reduction in power at\reynoldsnumber=165 compared to \reynoldsnumber=2230.

@@

 The data presented in Fig.\ref{fig:uncollapsed_data} for various damping ratios, $\zeta$, can be collapsed into a single line for a for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve). These collapsed curves were  obtained for the velocity amplitude  and power by plotting as functions of as a function of  the non dimensionalised  damping constant $c\rho\mathcal{A}U$ 
(Fig \ref{fig:collpased_data} (a),(b),(c) and (d)).  This further emphasizes that the galloping system is not frequency dependent. It is possible to obtain a different similar power output at different values of \ustar when the damping constant, $c\rho\mathbb{A}U$, is kept fixed. An example of this case, as shown in Fig.\ref{fig:time_hostory_velocity_same_power}, clearly show that this is a result of similar velocity amplitudes between cases if one were to disregard the high frequencies due to shedding. As mentioned earlier, it is the transverse velocity that determines the energy provided by the fluid forcing and the mechanical damping.

@@

 Power could be expressed as the product of force and velocity. Therefore the transferred power form fluid-to-body could be expressed as $P_t=F_y\dot{y}$. Similarly the dissipated power due to the mechanical damping could be expressed as $P_d=(c\dot{y})\dot{y}$. The time average of these two quantities should be equal due to energy conservation, provided that the mechanical friction is neglected . Analysing the  time histories of $P_t $ and $P_d$ at key regions (Fig.\ref{fig:regions_1}) on the mean power vs $U^*$ provides a detailed explanation for the variation of the output power when the reduced velocity is increased. The key regions consists of region 1 where the $P_{mean}$ increases with \ustar, region 2 where $P_{mean}$ becomes maximum and region 3 where $P_{mean}$ decreases with \ustar. It has been established earlier that the damping factor is a function of $U^*$. Therefore it could be derived that $U^*$ is inversely proportional to damping coefficient. Hence the damping coefficient reduces when you move from region 1 to 3.Fig \ref{fig:lift_curves} (a) shows that $C_y$ and therefore instantaneous force rises until $4^0$ where it peaks and then falls and at around $6^0$ becomes negative. Maximum amount of power could be transferred within the peak region. At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$. Data at $\zeta=0.1$, $m^*=40$ and \reynoldsnumber=165 (Fig.\ref{fig:power_time_histories}) are analysed as and example.

@@

 At region 1 where $U^*=90$ the damping constant is high and a clear sinusoidal signal could be observed for both $P_d$ and $P_t$ in Fig. \ref{fig:power_time_histories} (a). Fig.\ref{fig:power_time_histories} (d) and (g) shows that $\theta$ is in line or in phase with $F_y$.  The velocity amplitude in this case is small and the equivalent incident angle within the range where the hydrodynamic force increases with the incident angle (i.e. $0<\theta \leq < 4^0$ in Fig.\ref{fig:lift_curves} (a)) Hence both $P_d$ and $P_t$ becomes sinusoidal. In this case, power output is limited by the low fluid forces present at low incident angles. In other words damping is significantly high and extracts a lot of power that the velocity amplitude could not grow where the forcing  is significant to produce high level of power.

  At region 3 ($U^*= 400$) `$c$' is low in comparison with region 1 and 2 which leads to a low mean power output. Fig.\ref{fig:power_time_histories} (c) shows that $P_t$ becomes negative over some portion of the cycle. This is because $\theta$  passes the point where both $\theta$ and $C_y$ (therefore $F_y$) are positive. The high velocity amplitude leads to the equivalent incident angle $\theta$, in this case to exceed the range where $C_y$ is positive (i.e. $0<\theta<6^0$ in Fig.\ref{cy ploynomial} (a)). In this portion of the cycle the hydrodynamic force actually opposes the direction of travel and power is transferred from the structure to the fluid during those times. From and energy perspective, the mechanical damping is not sufficient to remover the energy transferred from the fluid to the structure during other times of the cycle because $c\rho\mathcal{A}U$ is substantially low. Therefore this excess energy is transferred back to the fluid as depicted by the negative region of $P_d$ in Fig.\ref{fig:power_time_histories} (c)

@@

The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}) was constant beyond $m^*=30$. However, at $m^* \leq 30$ an effect of $m^*$ it could be observed. Not only the peak value but overall reduction in the mean power could be observed when $m^*$ was reduced. When the galloping excitation is suppressed at low $m^*$, the system will exhibit a weak response as a result of forcing from vortex shedding. This was also reported by \cite{Joly2012} where galloping amplitude was reduced at low $m^*$. The suppression of galloping as $m^*$ is reduced can be explained by looking at the difference between the instantaneous power transfer between fluid to the structure $P_t$ and the power taken out by the mechanical damping $P_d$ in Fig.\ref{fig:power_time_histories}. While the time average of both quantities are the same, instantaneously they are not. Therefore the mechanical system is required to store power in certain points of the cycle and release it at another portion of the cycle. In cases where $m^*$ is very low, the system lack adequate inertia to store this power which leads to suppression of galloping.

@@

\subsection{Comparison with FSI simulations}
 Similar trends were captured for both displacement and velocity amplitudes between QSS and FSI simulations (Fig. \ref{fig:FSI_QSS_compare}(a) and \ref{fig:FSI_QSS_compare}(b)). Quantitatively a large discrepancy (average of $30\%$) could be observed between QSS and FSI data. Therefore the power also becomes significantly low in FSI data (Fig.\ref{fig:FSI_QSS_compare} (c)). However, the FSI data (Fig.\ref{fig:FSI_QSS_compare} (c)) were able to produce the main the rise and the fall of mean power when $U^*$ was increased. The reasoning behind this fact is that galloping is weak at \reynoldsnumber$=165$  and therefore fluid damping has a significant effect. It was reported by \cite{Barrero-Gil2009} that galloping only starts to occur ar Re $\geq 159$. As power is function of $(\dot{y})^2$ the error between QSS and FSI power becomes significantly large.
